\documentclass[a4paper,10pt]{article}
\input{glyphtounicode}
\pdfgentounicode=1
\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\geometry{margin=0.35in}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.2\textwidth}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{4pt}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.7}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}
% chktex 8


\begin{document}


\pagestyle{empty}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%----------Header--------------


  \begin{tabularx}{\linewidth}{@{} C @{}}

    \Huge{Vaibhav Magadum} \\[7.5pt]

    \href{https://github.com/Vaibhav-Magadum}{\raisebox{-0.05\height}\faGithub\ Vaibhav-Magadum} \ $|$ \ 
    \href{https://www.linkedin.com/in/vaibhav-magadum-444817265/}{\raisebox{-0.05\height}\faLinkedin\ Vaibhav Magadum} \ $|$ \  \ 
    \href{mailto:vaibhavmagadum859@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ vaibhavmagadum859@gmail.com} \ $|$ \ 
    \href{tel:+919380222052}{\raisebox{-0.05\height}\faMobile \ +91 9380222052}
    \\
  \end{tabularx}


%----------Education-----------


  \section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Dayananda Sagar College Of Engineering}{SGPA: 9.1}%
        {B.E in Information Science (VTU)}{2022 -- 2026}
        \hspace{4pt}
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
      \resumeSubheading
        {Jawahar Navodaya Vidaylaya}{87.6\%}
        {CBSE --- Higher Secondary/Senior School}{2020 -- 2022} \\
    \resumeSubHeadingListEnd
  \vspace{-15pt}


%----------Skills--------------

\vspace{6pt}
  \section{Skills}
  \begin{tabularx}{\linewidth}{@{}l X@{}}
    \textbf{Languages:} &  \normalsize{Python, C, C++, JavaScript } \\
    \textbf{Frameworks/Technologies:}  &  \normalsize{Linux, Git, Github, Flask, VS Code, Docker,React}\\
  \end{tabularx}
  \vspace{-5pt}




%----------Projects------------


  \section{Projects}
    
    \vspace{7pt}
    
  \begin{tabularx}{\linewidth}{ @{}l r@{} }
  \vspace{-5pt}
    \textbf{Restaurant Management System} \textit{} & \hfill \href{https://github.com/Vaibhav-Magadum/Restaurant-Management-System}{Restaurant Management System}\\
    \multicolumn{1}{@{}X@{}}{
    \begin{itemize}
        \item Showcase of personal and professional projects.
    \end{itemize}} \vspace{-7pt} \\

    \vspace{-5pt}
    \textbf{Project Zeta}|\textit{Flask, Supabase} & \hfill \href{https://projectzeta.vercel.app/}{Deployed} \\
    \multicolumn{1}{@{}X@{}}{
    \begin{itemize}
        \item A web platform for teachers where they can create their own ctf like challenges.
        \item Utilized Flask for backend and Supabase for database.
        \item Proof of concept for a new way of teaching cybersecurity using a gamified approach.
    \vspace{-10pt} 
        \end{itemize} 
        \vspace{-7pt} 
        }  \\

\vspace{-5pt}
    \textbf{Smart Traffic Management System} | \textit{Python, Pyfirmata, ftplib} & \hfill \href{https://github.com/Vaibhav-Magadum/MiniProject}{GitHub} \\
      \multicolumn{1}{@{}X@{}}{
        \begin{itemize}
            \item Utilized computer vision (yolo v8) for adaptive traffic signal control and real-time traffic density calculation.
            \item Utilized Arduino Uno to control traffic lights, enhancing traffic management and signal synchronization.
            \item Implemented WLAN data transfer using FTP to send real-time traffic density information for signal and data logging and utilized parallel computing for efficient data processing and traffic management \vspace{-10pt} 
        \end{itemize}
            }  \\


  \end{tabularx}


%----------Achievements---------


  \section{Achievements and Certifications}


    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{Google Cybersecurity} & \hfill \href{https://www.coursera.org/account/accomplishments/professional-cert/GZJ7LQGCFFZF}{Coursera (Mar 2024)}
      \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{An eight course professional certificate program in cybersecurity. Equipped with skills in threat detection, incident response, network security, python automation, SQL etc. }
    \end{tabularx}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{WordPress } & \hfill \href{The%20%22WordPress%20for%20Beginners:%20Step%20by%20Step%20Tutorial%20(2024)%22%20course%20on%20Eduta.org%20teaches%20beginners%20how%20to%20set%20up,%20customize,%20and%20manage%20WordPress%20sites,%20including%20themes,%20plugins,%20and%20essential%20site%20functionalities.}{Eduta (May 2024)}
      \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{-	The WordPress course on Eduta.org teaches beginners how to set up, customize, and manage WordPress sites, including themes, plugins, and essential site functionalities. }
    \end{tabularx}

